XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-25 talk/icooolps2011/paper.tex
fix references

The paper is structured as follows: Section~\ref{sec:background} gives an
introduction to the PyPy project and meta-tracing and presents an example of a
tiny dynamic language object model. Section~\ref{sec:hints} presents the hints,
what they do and how they are applied. Section~\ref{sec:fastobjmodel} shows how
the hints are applied to the tiny object model and Section~\ref{sec:evaluation}
presents benchmarks.

@@

\subsection{The PyPy Project}
\label{sect:pypy}

@@

%___________________________________________________________________________
\subsection{PyPy's Meta-Tracing JIT Compilers}
\label{sect:tracing}

@@

The trace would look like in Figure~\ref{fig:trace1}. In this example, the
attribute \texttt{a} is found on the instance, but the
attributes \texttt{b} and \texttt{c} are found on the class. The numbers line
numbers in the trace correspond to the line numbers in
Figure~\ref{fig:interpreter-slow} where the traced operations come from. The
trace indeed contains
five calls to \texttt{dict.get}, which is slow. To make the language efficient
using a tracing JIT, we need to find a way to get rid of these dictionary
lookups somehow. How to achieve this will be topic of
Section~\ref{sec:putting}.

>>>>

The paper is structured as follows: Section~\ref{sec:Background} gives an
introduction to the PyPy project and meta-tracing and presents an example of a
tiny dynamic language object model. Section~\ref{sec:hints} presents the hints,
what they do and how they are applied. Section~\ref{sec:fastobjmodel} shows how
the hints are applied to the tiny object model and Section~\ref{sec:evaluation}
presents benchmarks.

@@

\subsection{The PyPy Project}
\label{sub:pypy}

@@

%___________________________________________________________________________
\subsection{PyPy's Meta-Tracing JIT Compilers}
\label{sub:tracing}

@@

The trace would look like in Figure~\ref{fig:trace1}. In this example, the
attribute \texttt{a} is found on the instance, but the
attributes \texttt{b} and \texttt{c} are found on the class. The numbers line
numbers in the trace correspond to the line numbers in
Figure~\ref{fig:interpreter-slow} where the traced operations come from. The
trace indeed contains
five calls to \texttt{dict.get}, which is slow. To make the language efficient
using a tracing JIT, we need to find a way to get rid of these dictionary
lookups somehow. How to achieve this will be topic of
Section~\ref{sec:fastobjmodel}.
